Draft_markdown_v1

### 2024-04-08 Draft_V1.Rmd
Update Draft_V1.Rmd

---
title: "Draft_markdown_v1"
author: "River Kim"
date: "2024-04-07"
output: html_document
---

@@

```{r, eval=FALSE}
# Data importing (Following Course Book "Assessment Data")
library(ggplot2)
library(plyr)
library(gdata)
library(stringr)
library(data.table)

## Prep Osnabrugge et al.
data = fread("/Users/garamkim/Downloads/dataverse_files/uk_data.csv", encoding="UTF-8")
data$date = as.Date(data$date)

@@

```{r, eval=FALSE}
#Filtering data columns
library(tidyverse)
library(readr)
library(tidytext)
library(quanteda)
library(textdata)

colnames(data)
data <- data %>%
  select(last_name, first_name, date, female, age, party, text)
head(data)
```

@@

```{r, eval=FALSE}
# Filtering data containing immigration related words
# Define the keywords to search for
immig_words <- c('immigration', 'immigrant', 'asylum')
visa_words <- "\\b(UK)?visas?\\b"
all_words <- paste0(c(paste0(immig_words, collapse = "|"), visa_words), collapse = "|")

@@

```{r, eval=FALSE}
# Make 'Year' using 'date'
tidy_data_notoken$Year <- format(as.Date(tidy_data_notoken$date), "%Y")
data$Year <- format(as.Date(data$date), "%Y")

@@

```{r,eval=FALSE}
# Plotting counts of immigration texts by party
ggplot(text_count, aes(x = Year, y = n, group = party, color = party)) +
  geom_line() +
  labs(y = "Immigration texts num", x = "Year") +
  scale_x_continuous(breaks = seq(min(text_count$Year), max(text_count$Year), by = 4))
  theme_minimal()
```

@@

```{r,eval=FALSE}
# Count the total number of texts in data by year and party
data_count <- data %>%
  group_by(Year, party) %>%
  summarise(total_n = n(), .groups = 'drop')

@@

```{r,eval=FALSE}
#Plotting the ratios
ggplot(filtered_ratio_count, aes(x = Year, y = ratio, group = party, color = party)) +
  geom_line() +
  labs(y = "% Immigration Texts (n>100)", x = "Year") +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0), limits = c(0, NA)) +
  scale_x_continuous(breaks = seq(min(filtered_ratio_count$Year), max(filtered_ratio_count$Year), by = 4)) +
  theme_minimal()
```

@@

```{r,eval=FALSE}
# Tokenisation & removing stop words
tidy_data <- tidy_data_notoken %>%
  unnest_tokens(word, desc) %>%
  filter(str_detect(word, "[a-z]")) %>%
  filter(!word %in% stop_words$word)

tidy_data <- tidy_data %>%
  arrange(date)
tidy_data$order <- 1:nrow(tidy_data) # Make orders of each word

# Common tokens
word_count <- tidy_data %>%
  count(word, sort = T)

@@

```{r,eval=FALSE}
get_sentiments("nrc")

@@

```{r,eval=FALSE}
# Total sentiment of text including immigration related words plot
nrc_data %>%
  ggplot(aes(date, ratio)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", alpha=0.5) +
  labs(y = "Total NRC sentiment negative ratio", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red") +
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
```

@@

```{r,eval=FALSE}
# Arranging data by party and calculate the ratio of negative sentiment.
nrc_data_party <- tidy_data %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  group_by(party, date) %>%
  count(sentiment) %>%
  spread(key = sentiment, value = n, fill = 0) %>%
  mutate(ratio = negative/(positive+1)) %>%
  ungroup()

@@

```{r,eval=FALSE}
# A negative sentiment ratio plot of four parties
filtered_nrc_data_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.5, size = 1) +
  geom_smooth(method="loess", se = F, alpha=0.7, size = 1) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(y = "NRC Sentiment Negative Ratio by Party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red", size = 1) +
  annotate("text", x = as.Date("2007-09-24"), y = 4, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r,eval=FALSE}
# Faceting by party
filtered_nrc_data_party %>%
  ggplot(aes(x = date, y = ratio, color = party)) +
  geom_point(alpha = 0.5, size = 2) +
  geom_smooth(method = "loess", se = FALSE, alpha = 0.7, size = 1) +
  labs(y = "NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r,eval=FALSE}
# Total sentiment word counts by party
dominant_senti_nrc_party <-filtered_nrc_data_party %>%
  group_by(party) %>%
  summarise(across(c(anger, anticipation, disgust, fear, joy, sadness, surprise, trust, negative, positive), sum, na.rm = T))

@@

```{r,eval=FALSE}
# Combining all sentiments into one column
long_nrc_data <- filtered_nrc_data_party %>%
  pivot_longer(cols = c(anger, fear, trust, sadness, disgust, anticipation, surprise, joy), names_to = "sentiment", values_to = "score")
```

@@

```{r,eval=FALSE}
# Plotting specific sentiment changes by party
long_nrc_data %>%
  ggplot(aes(x = date, y = score, color = sentiment)) +
  geom_smooth(method = "loess", se = F, alpha = 1, size = 1) +
  geom_point(alpha = 0.5, size = 0.5) + 
  facet_wrap(~ party, scales = "free_y") +
  labs(x = "Date", y = "Score") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r,eval=FALSE}
# Shaping sentiment points differently
shape_mapping <- c("anger" = 17, "disgust" = 18, "fear" = 19, "sadness" = 8, "trust" = 21, "anticipation" = 22, "surprise" = 23, "joy" = 24)

@@

```{r,eval=FALSE}
# Specifying negative feelings only
long_nrc_data_neg <- filtered_nrc_data_party %>%
  pivot_longer(cols = c(anger, fear, sadness, disgust), names_to = "sentiment_negative", values_to = "score")

@@

```{r,eval=FALSE}
# Random sampling
data_sample <- data %>%
  sample_n(10000)

@@

```{r,eval=FALSE}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r,eval=FALSE}
# Faceting plots by party
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = F, alpha = 0.7, size = 1) +
  labs(y = "Sample NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r,eval=FALSE}
# Set up
library(text2vec) 
library(stringr)
library(umap) 
library(ggrepel)
```

@@

@@

```{r,eval=FALSE}
# choice parameters
WINDOW_SIZE <- 6 # context up to 6 words
DIM <- 300 # the length of the word vector
ITERS <- 100 # the maximum number of iterations
COUNT_MIN <- 10 # minimum count of words

@@

```{r,eval=FALSE}
#set model parameters
glove <- GlobalVectors$new(rank = DIM, x_max = 100, learning_rate = 0.05)

@@

@@

```{r,eval=FALSE}
# GloVe dimension reduction (two dimension)
glove_umap <- umap(glove_embedding, n_components = 2, metric = "cosine", n_neighbors = 25, min_dist = 0.1, spread=2)

@@

```{r,eval=FALSE}
word <- glove_embedding["immigration",, drop = FALSE]
cos_sim = sim2(x = glove_embedding, y = word, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words <- df_glove_umap %>% 
  inner_join(y=select, by= "word")

#The ggplot visual for GloVe
ggplot(selected_words, aes(x = UMAP1, y = UMAP2)) + 
      geom_point(show.legend = FALSE) + 
      geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
      labs(title = "GloVe word embedding of words related to 'immigration'") +
      theme(plot.title = element_text(hjust = .5, size = 14))
```

## 2) Training by party and pre/post economic crisis

@@

```{r,eval=FALSE}
library(RcppParallel)

@@

### (1) The GloVe model for *Conservative party before the 2008 economic crisis*

@@

```{r,eval=FALSE}
set.seed(42L)
glove_text_conser_pre <- sample(data_conser_pre$desc)

>>>>

---
title: "Draft_markdown_v1"
author: "River Kim"
date: "2024-04-07"
output:
  html_document: default
  word_document: default
---

@@

Data importing (Following Course Book "Assessment Data")

```{r}
library(ggplot2)
library(plyr)
library(gdata)
library(stringr)
library(data.table)
```

```{r}
## Prep Osnabrugge et al.
data = fread("/Users/garamkim/Downloads/dataverse_files/uk_data.csv", encoding="UTF-8")
data$date = as.Date(data$date)

@@

```{r}
library(tidyverse)
library(readr)
library(tidytext)
library(quanteda)
library(textdata)
```

```{r}
#Filtering data columns
colnames(data)
data <- data %>%
  select(last_name, first_name, date, female, age, party, text)
head(data)
```

@@

```{r}
# Filtering data containing immigration related words
# Define the keywords to search for
immig_words <- c('immigration', 'immigrant', 'asylum')
visa_words <- "\\b(UK)?visas?\\b"
all_words <- paste0(c(paste0(immig_words, collapse = "|"), visa_words), collapse = "|")

@@

```{r}
# Make 'Year' using 'date'
tidy_data_notoken$Year <- format(as.Date(tidy_data_notoken$date), "%Y")
data$Year <- format(as.Date(data$date), "%Y")

@@

```{r}
# Plotting counts of immigration texts by party
ggplot(text_count, aes(x = Year, y = n, group = party, color = party)) +
  geom_line() +
  labs(y = "Immigration texts num", x = "Year") +
  scale_x_continuous(breaks = seq(min(text_count$Year), max(text_count$Year), by = 4))
  theme_minimal()
```

@@

```{r}
# Count the total number of texts in data by year and party
data_count <- data %>%
  group_by(Year, party) %>%
  summarise(total_n = n(), .groups = 'drop')

@@

```{r}
#Plotting the ratios
ggplot(filtered_ratio_count, aes(x = Year, y = ratio, group = party, color = party)) +
  geom_line() +
  labs(y = "% Immigration Texts (n>100)", x = "Year") +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0), limits = c(0, NA)) +
  scale_x_continuous(breaks = seq(min(filtered_ratio_count$Year), max(filtered_ratio_count$Year), by = 4)) +
  theme_minimal()
```

@@

```{r}
# Tokenisation & removing stop words
tidy_data <- tidy_data_notoken %>%
  unnest_tokens(word, desc) %>%
  filter(str_detect(word, "[a-z]")) %>%
  filter(!word %in% stop_words$word)

tidy_data <- tidy_data %>%
  arrange(date)
tidy_data$order <- 1:nrow(tidy_data) # Make orders of each word
```

```{r}
# Common tokens
word_count <- tidy_data %>%
  count(word, sort = T)

@@

```{r}
get_sentiments("nrc")

@@

```{r}
# Total sentiment of text including immigration related words plot
nrc_data %>%
  ggplot(aes(date, ratio)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", alpha=0.5) +
  labs(y = "Total NRC sentiment negative ratio", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red") +
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
```

@@

```{r}
# Arranging data by party and calculate the ratio of negative sentiment.
nrc_data_party <- tidy_data %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  group_by(party, date) %>%
  count(sentiment) %>%
  spread(key = sentiment, value = n, fill = 0) %>%
  mutate(ratio = negative/(positive+1)) %>%
  ungroup()

@@

```{r}
# A negative sentiment ratio plot of four parties
filtered_nrc_data_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.5, size = 1) +
  geom_smooth(method="loess", se = F, alpha=0.7, size = 1) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(y = "NRC Sentiment Negative Ratio by Party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red", size = 1) +
  annotate("text", x = as.Date("2007-09-24"), y = 4, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r}
# Faceting by party
filtered_nrc_data_party %>%
  ggplot(aes(x = date, y = ratio, color = party)) +
  geom_point(alpha = 0.5, size = 2) +
  geom_smooth(method = "loess", se = FALSE, alpha = 0.7, size = 1) +
  labs(y = "NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r}
# Total sentiment word counts by party
dominant_senti_nrc_party <-filtered_nrc_data_party %>%
  group_by(party) %>%
  summarise(across(c(anger, anticipation, disgust, fear, joy, sadness, surprise, trust, negative, positive), sum, na.rm = T))

@@

```{r}
# Combining all sentiments into one column
long_nrc_data <- filtered_nrc_data_party %>%
  pivot_longer(cols = c(anger, fear, trust, sadness, disgust, anticipation, surprise, joy), names_to = "sentiment", values_to = "score")
```

@@

```{r}
# Plotting specific sentiment changes by party
long_nrc_data %>%
  ggplot(aes(x = date, y = score, color = sentiment)) +
  geom_smooth(method = "loess", se = F, alpha = 1, size = 1) +
  geom_point(alpha = 0.5, size = 0.5) + 
  facet_wrap(~ party, scales = "free_y") +
  labs(x = "Date", y = "Score") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r}
# Shaping sentiment points differently
shape_mapping <- c("anger" = 17, "disgust" = 18, "fear" = 19, "sadness" = 8, "trust" = 21, "anticipation" = 22, "surprise" = 23, "joy" = 24)

@@

```{r}
# Specifying negative feelings only
long_nrc_data_neg <- filtered_nrc_data_party %>%
  pivot_longer(cols = c(anger, fear, sadness, disgust), names_to = "sentiment_negative", values_to = "score")

@@

```{r}
# Random sampling
data_sample <- data %>%
  sample_n(10000)

@@

```{r}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r}
# Faceting plots by party
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = F, alpha = 0.7, size = 1) +
  labs(y = "Sample NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r}
# Set up
library(text2vec) 
library(stringr)
library(umap) 
library(ggrepel)
```

@@

### (1) The GloVe model for total parliament speech

@@

```{r}
# choice parameters
WINDOW_SIZE <- 6 # context up to 6 words
DIM <- 300 # the length of the word vector
ITERS <- 100 # the maximum number of iterations
COUNT_MIN <- 10 # minimum count of words

@@

```{r}
#set model parameters
glove <- GlobalVectors$new(rank = DIM, x_max = 100, learning_rate = 0.05)

@@

Modelling takes time. So I will use the prepared model made by same process for knitting.

```{r}
url <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove.rds?raw=true"
golve_embedding <- readRDS(url(url, method = "libcurl"))
```

@@

```{r}
# GloVe dimension reduction (two dimension)
glove_umap <- umap(glove_embedding, n_components = 2, metric = "cosine", n_neighbors = 25, min_dist = 0.1, spread=2)

@@

```{r}
word <- glove_embedding["immigration",, drop = FALSE]
cos_sim = sim2(x = glove_embedding, y = word, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words <- df_glove_umap %>% 
  inner_join(y=select, by= "word")
```

The ggplot visual for GloVe

```{r}
ggplot(selected_words, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "GloVe word embedding of words related to 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Total parliament speech word embedding of words related to *immigrants*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case2: immigrants)
word_2 <- glove_embedding["immigrants",, drop = FALSE]
cos_sim = sim2(x = glove_embedding, y = word_2, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_2 <- df_glove_umap %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_2, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Total parliament immigration related speech word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylums)
word_3 <- glove_embedding["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding, y = word_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_3 <- df_glove_umap %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_3, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Total parliament immigration related speech word embedding of words related to *asylum*

```{r}
# Plot the word embedding of words that are related for the GloVe model (asylum)
word_4 <- glove_embedding["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding, y = word_4, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_4 <- df_glove_umap %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_4, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

### (2) The Glove model for total Parliament speech before the 2008 economic crisis

```{r}
# filter data by date. Now have pre/post economic crisis text data related to immigration.

data_pre <- filter(tidy_data_notoken, date < as.Date("2007-09-24"))
data_post <- filter(tidy_data_notoken, date >= as.Date("2007-09-24"))
```

```{r}
set.seed(42L)
glove_text_pre <- sample(data_pre$desc)

tokens_pre <- space_tokenizer(glove_text_pre)
it_pre <- itoken(tokens_pre, progressbar = FALSE)
vocab_pre <- create_vocabulary(it_pre)
vocab_pruned_pre <- prune_vocabulary(vocab_pre, term_count_min = COUNT_MIN)

vectorizer_pre <- vocab_vectorizer(vocab_pruned_pre)
tcm_pre <- create_tcm(it_pre, vectorizer_pre, skip_grams_window = WINDOW_SIZE, skip_grams_window_context = "symmetric", weights = rep(1, WINDOW_SIZE))

glove_pre <- GlobalVectors$new(rank = DIM, x_max = 100, learning_rate = 0.05)
word_vectors_main_pre <- glove_pre$fit_transform(tcm_pre, n_iter = ITERS, convergence_tol = 0.001, n_threads = RcppParallel::defaultNumThreads())

word_vectors_context_pre <- glove_pre$components
glove_embedding_pre <- word_vectors_main_pre + t(word_vectors_context_pre)

saveRDS(glove_embedding_pre, file = "local_glove_pre.rds")
```

Modelling takes time. So I will use the prepared model made by same process for knitting.

```{r}
url_pre <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_pre.rds?raw=true"
golve_embedding_pre <- readRDS(url(url_pre, method = "libcurl"))
```

Pre-crisis total GloVe word embedding two dimensional umap

```{r}
# Plotting the whole word embedding of pre-crisis immigration related text
umap_pre <- umap(glove_embedding_pre, n_components = 2, metric = "cosine", n_neighbors = 25, min_dist = 0.1, spread = 2)

df_umap_pre <- as.data.frame(umap_pre[["layout"]])
df_umap_pre$word <- rownames(df_umap_pre)
colnames(df_umap_pre) <- c("Pre_UMAP1", "Pre_UMAP2", "word")
```

```{r}
ggplot(df_umap_pre) +
  geom_point(aes(x = Pre_UMAP1, y = Pre_UMAP2), color = 'blue', size = 0.05) +
  labs(title = "(Pre-crisis) GloVe word embedding of words related to 'immigration'") +
  theme_minimal()
```

Pre-crisis total parliament speech word embedding of words related to *immigration*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case1: immigration)
word_pre_1 <- glove_embedding_pre["immigration",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_pre, y = word_pre_1, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_pre_1 <- df_umap_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_1, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Pre-crisis total parliament speech word embedding of words related to *immigrants*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case2: immigrants)
word_pre_2 <- glove_embedding_pre["immigrants",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_pre, y = word_pre_2, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_pre_2 <- df_umap_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_2, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Pre-crisis total parliament speech word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylums)
word_pre_3 <- glove_embedding_pre["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_pre, y = word_pre_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_pre_3 <- df_umap_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_3, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Pre-crisis total parliament speech word embedding of words related to *asylum*

```{r}
# Plot the word embedding of words that are related for the GloVe model (asylum)
word_pre_4 <- glove_embedding_pre["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_pre, y = word_pre_4, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_pre_4 <- df_umap_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_4, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

### (3) The Glove model for total Parliament speech after the 2008 economic crisis

```{r}
set.seed(42L)
glove_text_post <- sample(data_post$desc)

tokens_post <- space_tokenizer(glove_text_post)
it_post <- itoken(tokens_post, progressbar = FALSE)
vocab_post <- create_vocabulary(it_post)
vocab_pruned_post <- prune_vocabulary(vocab_post, term_count_min = COUNT_MIN)

vectorizer_post <- vocab_vectorizer(vocab_pruned_post)
tcm_post <- create_tcm(it_post, vectorizer_post, skip_grams_window = WINDOW_SIZE, skip_grams_window_context = "symmetric", weights = rep(1, WINDOW_SIZE))

glove_post <- GlobalVectors$new(rank = DIM, x_max = 100, learning_rate = 0.05)
word_vectors_main_post <- glove_post$fit_transform(tcm_post, n_iter = ITERS, convergence_tol = 0.001, n_threads = RcppParallel::defaultNumThreads())

word_vectors_context_post <- glove_post$components
glove_embedding_post <- word_vectors_main_post + t(word_vectors_context_post)

saveRDS(glove_embedding_post, file = "local_glove_post.rds")
```

Modelling takes time. So I will use the prepared model made by same process for knitting.

```{r}
url_post <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_post.rds?raw=true"
golve_embedding_post <- readRDS(url(url_post, method = "libcurl"))
```

Pre-crisis total GloVe word embedding two dimensional umap

```{r}
# Plotting the whole word embedding of pre-crisis immigration related text
umap_post <- umap(glove_embedding_post, n_components = 2, metric = "cosine", n_neighbors = 25, min_dist = 0.1, spread = 2)

df_umap_post <- as.data.frame(umap_post[["layout"]])
df_umap_post$word <- rownames(df_umap_post)
colnames(df_umap_post) <- c("Post_UMAP1", "Post_UMAP2", "word")
```

```{r}
ggplot(df_umap_post) +
  geom_point(aes(x = Post_UMAP1, y = Post_UMAP2), color = 'blue', size = 0.05) +
  labs(title = "(Post-crisis) GloVe word embedding of words related to 'immigration'") +
  theme_minimal()
```

Pre-crisis total parliament speech word embedding of words related to *immigration*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case1: immigration)
word_post_1 <- glove_embedding_post["immigration",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_post, y = word_post_1, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_post_1 <- df_umap_post %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_1, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Pre-crisis total parliament speech word embedding of words related to *immigrants*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case2: immigrants)
word_post_2 <- glove_embedding_post["immigrants",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_post, y = word_post_2, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_post_2 <- df_umap_post %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_2, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Post-crisis total parliament speech word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylums)
word_post_3 <- glove_embedding_post["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_post, y = word_post_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_post_3 <- df_umap_post %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_3, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Post-crisis total parliament speech word embedding of words related to *asylum*

```{r}
# Plot the word embedding of words that are related for the GloVe model (asylum)
word_post_4 <- glove_embedding_post["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_post, y = word_post_4, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_post_4 <- df_umap_post %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_4, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

# 2) Training by party and pre/post economic crisis

@@

```{r}
library(RcppParallel)

@@

### (1) The GloVe model for Conservative party before the 2008 economic crisis

@@

```{r}
set.seed(42L)
glove_text_conser_pre <- sample(data_conser_pre$desc)
